---
title: "Who is Afraid of the Istanbul Convention? Explaining Opposition to and Support for Gender Equality"
date: 2024-10-24
author:
  - name: Andrea Krizsán
    url: https://people.ceu.edu/andrea_krizsan
    orcid: 0000-0002-8723-4023
    affiliation: Central European University, Vienna, Austria
  - name: Conny Roggeband
    url: https://www.uva.nl/en/profile/r/o/c.m.roggeband/c.m.roggeband.html
    orcid: 0000-0003-0060-734X
    affiliation: University of Amsterdam, Amsterdam, Netherlands
  - name: Michael C. Zeller
    url: https://michaelzeller.de/
    orcid: 0000-0002-2422-3896
    affiliation: Ludwig-Maximilians-Universität München, München, Germany
categories:
  - Istanbul convention
  - gender
  - violence
  - anti-gender mobilisation
  - qualitative comparative analysis (QCA)
  - process tracing
pub-info:
  reference: >-
    <a href="https://people.ceu.edu/andrea_krizsan">Andrea Krizsán</a>, <a href="https://www.uva.nl/en/profile/r/o/c.m.roggeband/c.m.roggeband.html">Conny Roggeband</a>, and <strong>Michael C. Zeller</strong>, “Who is Afraid of the Istanbul Convention? Explaining Opposition to and Support for Gender Equality,” <em>Comparative Political Studies</em> 0, no. 0 (2024): 1-41, doi: <a href="https://doi.org/10.1177/00104140241290205"><code>10.1177/00104140241290205</code></a>
  links:
  - name: PDF
    url: KrizsanRoggebandZeller2024-who-is-afraid-of-the-istanbul-convention-explaining-opposition-to-and-support-for-gender-equality.pdf
    local: true
    # icon: bi filetype-pdf
  - name: Online version
    url: https://doi.org/10.1177/00104140241290205
    # icon: fa-solid fa-scroll
  - name: Add to Zotero
    url: https://www.zotero.org/save?type=doi&q=10.1177/00104140241290205
    # icon: ai ai-zotero
  extra: >-
    Rotation principle. Each author contributed equally. We are indebted to Penelope Bollini for gathering much of the raw data. We thank Vera Messing for advice on relevant survey data. We also thank Ioana-Elena Oana and Carsten Q. Schneider for guidance on applying their QCA robustness test protocol. 
doi: 10.1177/00104140241290205
haiku:
  - <em>"... four pathways for ratification, driven by feminist egalitarian norms, international conditionality, pro-European governments at odds with social opposition, and societies unwilling to mobilize for conservative religious institutions."</em>
---

## Important links

- [Full article](KrizsanRoggebandZeller2024-who-is-afraid-of-the-istanbul-convention-explaining-opposition-to-and-support-for-gender-equality.pdf)
- My co-authors, Andrea Krizsan and Conny Roggeband, have written a short blog summary of our article for *The Loop*: <https://theloop.ecpr.eu/whos-afraid-of-the-istanbul-convention-understanding-the-debate-over-gender-equality-in-europe/>

## Abstract

Across Europe, contention has emerged over the Istanbul Convention, a treaty combatting violence against women. The Convention has become a main arena for contention over gender and sexual equality. Right-wing forces mobilize nationally—and transnationally—to advocate for traditional values and oppose so-called ‘gender ideology’, while progressive actors resist efforts to curtail women’s rights. Consequently, while many have ratified the Convention, several countries have not. This article asks which causes motive ratification; which causes underlie non-ratification? We present a qualitative comparative analysis (QCA) on 40 European states to disentangle the causal complexity of ratification decisions. We identify four pathways for ratification, driven by feminist egalitarian norms, international conditionality, pro-European governments at odds with social opposition, and societies unwilling to mobilize for conservative religious institutions. We unpack these causal patterns in four minimalist case studies. The article reveals causation underlying contention between pro-gender, anti-gender, and state actors, and resultant policy outcomes.

## Important figures

<table>
  <caption>Ratification of the Istanbul Convention by Council of Europe member states (EU member states in <strong>bold</strong>). An asterisk indicates countries considering withdrawal from the IC; Two asterisks indicates countries withdrawn from the IC.</caption>
  <thead>
    <tr>
      <th><strong>Ratification status</strong></th>
      <th><strong>Countries</strong></th>
    </tr>
  </thead>
  <tbody>
    <tr>
      <td>Ratified in 2012</td>
      <td>Turkey**</td>
    </tr>
    <tr>
      <td>Ratified in 2013</td>
      <td>Albania, <strong>Austria</strong>, Bosnia and Herzegovina, <strong>Italy</strong>, Montenegro, <strong>Portugal</strong>, Serbia</td>
    </tr>
    <tr>
      <td>Ratified in 2014</td>
      <td>Andorra, <strong>Denmark</strong>, <strong>France</strong>, <strong>Malta</strong>, Monaco, <strong>Spain</strong>, <strong>Sweden</strong></td>
    </tr>
    <tr>
      <td>Ratified in 2015</td>
      <td><strong>Finland</strong>, <strong>Netherlands</strong>, <strong>Poland</strong>*, <strong>Slovenia</strong></td>
    </tr>
    <tr>
      <td>Ratified in 2016</td>
      <td><strong>Belgium</strong>, <strong>Romania</strong>, San Marino</td>
    </tr>
    <tr>
      <td>Ratified in 2017</td>
      <td><strong>Cyprus</strong>, <strong>Estonia</strong>, Georgia, <strong>Germany</strong>, Norway, Switzerland</td>
    </tr>
    <tr>
      <td>Ratified in 2018</td>
      <td><strong>Croatia</strong>, <strong>Greece</strong>, Iceland, <strong>Luxembourg</strong>, North Macedonia</td>
    </tr>
    <tr>
      <td>Ratified in 2019</td>
      <td><strong>Ireland</strong></td>
    </tr>
    <tr>
      <td>Ratified in 2022</td>
      <td>Ukraine, United Kingdom</td>
    </tr>
    <tr>
      <td>Not ratified as of March 2021</td>
      <td>Armenia, Azerbaijan, <strong>Bulgaria</strong>, <strong>Czechia</strong>, <strong>Hungary</strong>, <strong>Latvia</strong>, Lichtenstein, <strong>Lithuania</strong>, Moldova, Russia, <strong>Slovakia</strong></td>
    </tr>
  </tbody>
</table>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = F,
	message = FALSE,
	warning = FALSE,
	collapse = TRUE,
	comment = "#>"
)
library(dplyr)
library(ggplot2)
library(reshape2)
library(QCA)
library(SetMethods)

ICdata <- read.csv("database_IC-qca.csv", row.names=1, header = TRUE)
# ICdata <- read_excel("IC_QCA_data.xlsx", sheet = "database")

# Outcome -----------------------------------------------------------------

# IC (fuzzy) = full Istanbul Convention ratification
#### 1 - signed and ratified; 
#### 0.75 - signed and ratified with declaration; 
#### 0.25 - signed but not ratified; 
#### 0 - not signed/denounced

# Conditions --------------------------------------------------------------

# LDB - liberal democratic backsliding, using v2xlibdem variable (2021 score subtracted by 2013 score)
#### Calibration (direct method)
#### Robustness test w/ EDB, egalitarian democratic backsliding, using v2xegaldem variable (2021 score subtracted by 2013 score)
#### Robustness test w/ SLD, strong liberal democracy, using v2xlibdem variable (2021 score)
#### Robustness test w/ SED, strong egalitarian democracy, using v2xegaldem variable (2021 score)

# RGOV (fuzzy) = solid right-wing government (through signature and ratification phase) 
#### Calibration (direct assignment): 
#### 1    - solid right throughout signature and ratification; 
#### 0.75 - not solid right at signature, solid right since signature; 
#### 0.45 - solid right at signature, not solid right in post-signature; 
#### 0.25 - not solid right signature - left right changes afterwards; 
#### 0    - not solid right, neither at signature nor ratification

# OPPG - opposition to 'gender ideology'
#### Calibration (direct assignment): derived from unweighted index of EVS/ESS data,
#### A124_09 (EVS: homosexual neighbours are undesirable), 
#### D081_N (EVS: disagree that homosexuals are good parents), 
#### F118_N (EVS: homosexuality is never justifiable))

# HRM (crisp) = homogenous religious majority
#### if a country is predominantly Catholic, Orthodox, or Islamic (EVS: F025_MAJ), 
#### and if that predominance is over 50% of the population (A006), 
#### then the country is scored as 1; otherwise scored as 0

# WPOW - women's political empowerment: derived from unweighted index of V-Dem data
#### v2x_genpp_2020 (women’s political empowerment women's political participation) and
#### v2x_cspart (civil society participation)

# WEQU - strong social support for women’s equality
#### Calibration (direct assignment): derived from EVS/ESS data
#### C001 (EVS: men should have more right to a job than women)

ICdata$HRM <- ICdata$CATH_ORTH_MUSL

# TIDY THE DATA

# removing rows
row.names.remove <- c("Andorra", "Liechtenstein", "Luxembourg", "Malta", "Monaco", "Moldova", "San Marino")

ICdata <- ICdata[!(row.names(ICdata) %in% row.names.remove), ]

ICdatax <- ICdata[!(row.names(ICdata) %in% row.names.remove), ]

# removing excess columns
# ICdatax <- ICdatax[-c(2:7,24:106)]

# i. calibration ----------------------------------------------------------

# LDB: liberal democratic backsliding

# ICdatax$LDEMBACK <- ICdatax$v2x_libdem_2020 - ICdatax$v2x_libdem_2013
ICdatax$LDEMBACK <- ICdatax$v2x_libdem_2021 - ICdatax$v2x_libdem_2013

ICdatax$LDB <- calibrate(ICdatax$LDEMBACK,
                         type = "fuzzy",
                         thresholds = c(0, -0.08, -0.1))
ICdatax$LDB

# WPOW: women's political empowerment 
ICdatax$WOMPOW <- (ICdatax$v2x_gender_2020 + ICdatax$v2x_cspart_2020)/2

ICdatax$WPOW <- calibrate(ICdatax$WOMPOW,
                          type = "fuzzy",
                          thresholds = c(0.35, 0.9, 0.97))
ICdatax$WPOW

####
# alternative analysis conditions
####

# EDB: egalitarian democratic backsliding
#ICdatax$EDEMBACK <- ICdatax$v2x_egaldem_2020 - ICdatax$v2x_egaldem_2013
ICdatax$EDEMBACK <- ICdatax$v2x_egaldem_2021 - ICdatax$v2x_egaldem_2013

ICdatax$EDB <- calibrate(ICdatax$EDEMBACK,
                         type = "fuzzy",
                         thresholds = c(0.04, -0.065, -0.2))
ICdatax$EDB

# SLD: strong liberal democracy, v2xlibdem variable (2021 score)
ICdatax$SLD <- calibrate(ICdatax$v2x_libdem_2021,
                         type = "fuzzy",
                         thresholds = c(0.15, 0.775, 0.79))
ICdatax$SLD

# SED, strong egalitarian democracy, v2xegaldem variable (2021 score)
ICdatax$SED <- calibrate(ICdatax$v2x_egaldem_2021,
                         type = "fuzzy",
                         thresholds = c(0.25, 0.65, 0.85))
ICdatax$SED

# WPAR: women's political participation
ICdatax$WPAR <- calibrate(ICdatax$v2x_genpp_2020,
                          type = "fuzzy",
                          thresholds = c(0.8, 0.9945, 1))
ICdatax$WPAR



# iii. for table of all democracy conditions ------------------------------

ICdataDEM <- dplyr::select(ICdatax, c("LDB","EDB","SLD","SED"))

```


```{r IC-adoption-fig, fig.cap="Istanbul Convention adoption and solidly right-wing governments in 40 countries. Periods covered by a grey bar represent times when a solidly right-wing government was in power. $\\circ$ marks the date of signing the Convention. $\\smallblackdiamond$ marks the date of ratification. $\\times$ marks the date of Turkey's withdrawal.\\label{fig:IC-adoption}", out.width='99%'}
# out.extra='angle=90',
library(readxl)

govs <- read_excel("IC_graphics2022nov17.xlsx", range = "A1:I112")

govs$Order <- factor(govs$Order,
                       levels = c("1", "2", "3", "4", "5"))

ICgraphic <- ggplot(govs, aes(x=Country, y=Days, fill=Order)) +
  geom_bar(stat = "identity", width = 0.7, position = position_stack(reverse = T)) +
  scale_fill_manual("legend", values = c("1" = "grey50", "2" = "white", "3" = "grey50", "4" = "white", "5" = "grey50")) +
  scale_y_continuous("Year", breaks = seq(0,4015,365),
                     labels = paste0(c("2011","2012","2013","2014","2015","2016","2017","2018","2019","2020","2021","2022"))) +
  geom_point(aes(y=Signed), shape=1, size=2) +
  geom_point(aes(y=Ratified), shape=23, fill="black", size=2) +
  geom_point(aes(y=Withdrawn), shape=4, size=2) +
  coord_flip() +
  theme(
    # axis.ticks.y = element_blank(),
    # axis.text.y = element_text(hjust = 1.3),
    panel.background = element_rect(fill = NA),
    panel.ontop = TRUE,
    panel.grid.major.y = element_blank(),
    # explicitly set the horizontal lines (or they will disappear too)
    panel.grid.major.x = element_line(size=.2, color="black"),
    panel.grid.minor = element_blank(),
    legend.position = "none",
    axis.title.x = element_blank(),
    axis.title.y = element_blank()
  ) + 
  scale_x_discrete(limits=rev)
ICgraphic + geom_vline(xintercept = ((-0.51:39.51)+1), linewidth=0.5, color = "grey80")


```

<table>
  <caption>Summary of calibration strategy.</caption>
  <thead>
    <tr>
      <th><strong>Condition (abbreviation)</strong></th>
      <th><strong>Raw data source</strong></th>
      <th><strong>Range (min., mean, max.)</strong></th>
      <th><strong>Calibration method</strong></th>
      <th><strong>Calibration thresholds</strong></th>
      <th><strong>Set scores</strong></th>
    </tr>
  </thead>
  <tbody>
    <tr>
      <td>Liberal democracy backsliding (LDB)</td>
      <td>V-Dem (2013, 2021): <em>v2x_libdem</em></td>
      <td>-0.41, -0.035, 0.35</td>
      <td>direct</td>
      <td>full incl.: -0.1 <br> crossover: -0.08 <br> full excl.: 0</td>
      <td></td>
    </tr>
    <tr>
      <td>Solid right-wing government (RGOV)</td>
      <td>ParlGov</td>
      <td></td>
      <td>assignment</td>
      <td></td>
      <td><strong>1</strong>: all RW gov. <br> <strong>0.75</strong>: RW gov. after signing <br> <strong>0.45</strong>: RW gov. at signing, not after <br> <strong>0.25</strong>: some RW gov. after signing <br> <strong>0</strong>: no RW gov.</td>
    </tr>
    <tr>
      <td>Strong social opposition to gender equality (OPPG)</td>
      <td>European Values Survey (EVS), European Social Survey (ESS)</td>
      <td>0.04, 0.44, 0.93</td>
      <td>assignment</td>
      <td></td>
      <td><strong>1</strong>: strong opp. <br> <strong>0.66</strong>: fairly strong opp. <br> <strong>0.33</strong>: somewhat strong opp. <br> <strong>0</strong>: not strong opp.</td>
    </tr>
    <tr>
      <td>Homogenous religious majority (HRM)</td>
      <td>European Values Survey (EVS), European Social Survey (ESS)</td>
      <td></td>
      <td>assignment</td>
      <td></td>
      <td><strong>1</strong>: majority Catholic, Orthodox, or Islamic <br> <strong>0</strong>: no such majority</td>
    </tr>
    <tr>
      <td>Strong women's empowerment (WPOW)</td>
      <td>V-Dem (2020): index of <em>v2x_genpp</em> and <em>v2x_cspart</em></td>
      <td>0.97, 0.842, 0.35</td>
      <td>direct</td>
      <td>full incl.: 0.97 <br> crossover: 0.9 <br> full excl.: 0.35</td>
      <td></td>
    </tr>
    <tr>
      <td>Strong social support for women's equality (WEQU)</td>
      <td>European Values Survey (EVS), European Social Survey (ESS)</td>
      <td>0.02, 0.234, 0.57</td>
      <td>assignment</td>
      <td></td>
      <td><strong>1</strong>: strong support <br> <strong>0.66</strong>: fairly strong support <br> <strong>0.33</strong>: somewhat strong support <br> <strong>0</strong>: not strong support</td>
    </tr>
    <tr>
      <td>EU candidacy (EUC)</td>
      <td>2020 EU candidates list</td>
      <td></td>
      <td>assignment</td>
      <td></td>
      <td><strong>1</strong>: EU candidate <br> <strong>0</strong>: non-candidate</td>
    </tr>
  </tbody>
</table>


```{r necessity, fig.cap="Possible necessary disjunction representing ‘socio-political liberalism’ ($\\sim$RGOV + $\\sim$OPPG)\\label{fig:nec}", out.extra='angle=90', out.width='140%'}
ICdatay <- dplyr::select(ICdatax, c("IC","LDB","RGOV","OPPG","HRM","WPOW","WEQU",
                             "EUC"))

SUIN_I <- superSubset(data = ICdatay,
                       conditions = c("LDB","RGOV","OPPG","HRM","WPOW",
                                      "WEQU","EUC"),
                       outcome = "IC",
                       relation = "nec",
                       incl.cut = 0.9,
                       cov.cut = 0.6,
                       ron.cut = 0.5,
                       depth = 2)
# SUIN_I

SUIN_IC <- superSubset(data = ICdatay,
                       conditions = c("LDB","RGOV","OPPG","HRM","WPOW",
                                      "WEQU","EUC"),
                       outcome = "IC",
                       relation = "nec",
                       incl.cut = 0.94,
                       cov.cut = 0.6,
                       ron.cut = 0.5,
                       depth = 2)

# pimplot(data = ICdatay, results = SUIN_IC, outcome = "IC",necessity = TRUE, jitter = TRUE, font = "mono")

library(yarrr)

nec <- compute("~RGOV + ~OPPG", data = ICdatay) # compute nec. set membership scores
col <- rep(yarrr::transparent("white", trans.val = .9), nrow(ICdatay)) # define a vector of colors
col[nec > 0.5 & ICdatay$IC < 0.5] <- "grey70" # zone 4
col[nec < 0.5 & ICdatay$IC < 0.5] <- "grey70" # zone 4
col[nec < 0.5 & ICdatay$IC >= 0.5] <- "black" # zone 5
# col[nec > 0.5 & nec < 0.8 & ICdatay$IC > 0.5] <- "black"
clabels <- logical(nrow(ICdatay))
clabels[c(26)] <- TRUE # only these labels to print

# XYplot("~RGOV + ~OPPG", "IC", relation = "necessity", data = ICdatay, jitter = TRUE, amount = 0.03, clabels = clabels, xlab = "~RGOV + ~OPPG (socio-political liberalism?)", col = "black", bg = col)

# COLOUR VERSION
# nec <- compute("~RGOV + ~OPPG", data = ICdatay) # compute nec. set membership scores
# col <- rep("darkgreen", nrow(ICdatay)) # define a vector of colors
# col[nec < 0.5 & ICdatay$IC < 0.5] <- "blue" # zone 4
# col[nec < 0.5 & ICdatay$IC >= 0.5] <- "red" # zone 5
# clabels <- logical(nrow(ICdatay))
# clabels[c(26)] <- TRUE # only these labels to print
# 
# XYplot("~RGOV + ~OPPG", "IC", relation = "necessity", data = ICdatay, jitter = TRUE, amount = 0.03, clabels = clabels, xlab = "~RGOV + ~OPPG (socio-political liberalism?)", col = col, bg = col)

```


```{r tt, out.extra='angle=90', out.width='100%'}

ttIC <- truthTable(data=ICdatay, outcome = "IC",
                   conditions = c("LDB","RGOV","OPPG","HRM","WPOW","WEQU",
                                  "EUC"),
                   incl.cut=0.85,
                   sort.by=c("incl", "n"), 
                   complete=TRUE,
                   show.cases=TRUE, 
                   PRI=TRUE)
# ttIC

# stargazerTT(ttIC, show.cases = TRUE)

```


```{r upset-plot, echo=FALSE, fig.cap="Set intersections of QCA model. The light grey bars represent truth table rows with the outcome; dark grey without; the black bar represents the one contradictory truth table row (i.e., row 25).\\label{fig:upset}", out.width='99%'}

ICdataz <- subset(ICdatay, select = -c(IC))
ICdataz <- ifelse(ICdataz > 0.5, 1, 0)
ICvennZ <- as.data.frame(ICdataz)

library(ComplexUpset)
library(ggplot2)

upset(data = ICvennZ, 
      intersect = c("LDB", "RGOV", "OPPG", "HRM", "WPOW", "WEQU", "EUC"),
      base_annotations = list(
        'Intersection size'=(
          intersection_size(
            mapping=aes(fill='bars_color')) +
            scale_y_continuous(breaks=seq(0,10,1), limits=c(0,10)) +
            scale_fill_manual(values = c('bars_color'='black'), guide='none'))
      ),
      queries=list(upset_query(set='HRM', fill='black'),
                   upset_query(set='WEQU', fill='black'),
                   upset_query(set='OPPG', fill='black'),
                   upset_query(set='WPOW', fill='black'),
                   upset_query(set='LDB', fill='black'),
                   upset_query(set='EUC', fill='black'),
                   upset_query(set='RGOV', fill='black'),
                   upset_query(intersect=c('WPOW', 'WEQU'), 
                               color='black', fill='grey80', 
                               only_components=c('intersections_matrix', 'Intersection size')),
                   upset_query(intersect=c('HRM', 'OPPG', 'EUC'), 
                               color='black', fill='grey80', 
                               only_components=c('intersections_matrix', 'Intersection size')),
                   upset_query(intersect=c('LDB', 'OPPG', 'HRM'), 
                               color='black', fill='grey80', 
                               only_components=c('intersections_matrix', 'Intersection size')),
                   upset_query(intersect=c('OPPG', 'WPOW', 'WEQU'), 
                               color='black', fill='grey80', 
                               only_components=c('intersections_matrix', 'Intersection size')),
                   upset_query(intersect=c('LDB', 'HRM', 'WEQU'), 
                               color='black', fill='grey80', 
                               only_components=c('intersections_matrix', 'Intersection size')),
                   upset_query(intersect=c('LDB', 'OPPG', 'HRM', 'EUC'), 
                               color='black', fill='grey80', 
                               only_components=c('intersections_matrix', 'Intersection size')),
                   upset_query(intersect=c('LDB', 'OPPG', 'HRM', 'WPOW'), 
                               color='black', fill='grey80', 
                               only_components=c('intersections_matrix', 'Intersection size')),
                   upset_query(intersect=c('RGOV', 'OPPG', 'HRM', 'EUC'), 
                               color='black', fill='grey80', 
                               only_components=c('intersections_matrix', 'Intersection size')),
                   upset_query(intersect=c('HRM', 'WPOW', 'WEQU'), 
                               color='black', fill='grey80', 
                               only_components=c('intersections_matrix', 'Intersection size')),
                   upset_query(intersect=c('RGOV', 'WPOW', 'WEQU'), 
                               color='black', fill='grey80', 
                               only_components=c('intersections_matrix', 'Intersection size')),
                   upset_query(intersect=c('HRM', 'WPOW'), 
                               color='black', fill='grey80', 
                               only_components=c('intersections_matrix', 'Intersection size')),
                   upset_query(intersect=c('RGOV', 'HRM'), 
                               color='black', fill='grey80', 
                               only_components=c('intersections_matrix', 'Intersection size')),
                   upset_query(intersect=c('RGOV'), 
                               color='black', fill='grey50', 
                               only_components=c('intersections_matrix', 'Intersection size')),
                   upset_query(intersect=c('LDB', 'RGOV', 'OPPG'), 
                               color='black', fill='grey50', 
                               only_components=c('intersections_matrix', 'Intersection size')),
                   upset_query(intersect=c('RGOV', 'OPPG', 'WPOW'), 
                               color='black', fill='grey50', 
                               only_components=c('intersections_matrix', 'Intersection size')),
                   upset_query(intersect=c('RGOV', 'OPPG', 'HRM'), 
                               color='black', fill='grey50', 
                               only_components=c('intersections_matrix', 'Intersection size')),
                   upset_query(intersect=c('LDB', 'RGOV', 'OPPG', 'HRM', 'EUC'), 
                               color='black', fill='grey50', 
                               only_components=c('intersections_matrix', 'Intersection size'))),
      name = 'Intersections',
)
```

To produce the most parsimonious solution we reduce the complexity of the truth table. Minimization of our truth table produces four configurations of conditions that seemingly motivate ratification of the Istanbul Convention:

> WEQU + \sim LDB * EUC + LDB * \sim RGOV + \sim OPPG * HRM &rightarrow; IC

This expression reads as follows:

- strong social support for women’s equality (WEQU) or 
- not liberal democratic backsliding ($\sim$LDB) and EU candidacy (EUC) or 
- liberal democratic backsliding (LDB) and not solid right-wing government ($\sim$RGOV) or 
- not strong social opposition to gender ($\sim$OPPG) and a homogenous religious majority

are sufficient for Istanbul Convention ratification (IC). 


```{r sufficiency, fig.cap="Sufficiency solution.\\label{fig:sol-p-plot}", out.extra='angle=90', out.width='140%'}
sol_c <- minimize(ttIC, details=TRUE, show.cases=TRUE)
# sol_c

sol_i <- minimize(ttIC, details = TRUE, 
                  include = "?",
                  dir.exp = c(0, 0, 0, 0, 1, 1, 1))
# sol_i

# stargazerSol(sol_i,
#              outcome = "IC",
#              show.cases = T,
#              type = "latex",
#              title = "",
#              out = NULL,
#              digits = 3)

sol_p <- minimize(ttIC, include = "?",
                  details = TRUE, show.cases = TRUE)
# sol_p

## check EASY COUNTERFACTUALs made for sol_i
# sol_i$i.sol$C1P1$EC
# ...64 rows...
# sol_i$i.sol$C2P1$EC
# ...64 rows...

## check SIMPLIFYING ASSUMPTIONS made for sol_p
# sol_p$SA
# ...92 rows...


# pimplot(data = ttIC, results = sol_i, outcome = "IC", all_labels = TRUE, jitter = TRUE, font = "mono")

library(yarrr)
# i_sol <- compute("~LDB*EUC + LDB*~RGOV + ~LDB*~OPPG*HRM + ~LDB*~OPPG*WPOW*WEQU +
#        ~RGOV*~HRM*WPOW*WEQU", data = ICdatay) # compute sol_i set membership scores
p_sol <- compute("WEQU + ~LDB*EUC + LDB*~RGOV + ~OPPG*HRM", data = ICdatay) # compute sol_p set membership scores
col <- rep(yarrr::transparent("white", trans.val = .9), nrow(ICdatay)) # define a vector of colors
col[p_sol < 0.5 & ICdatay$IC < 0.5] <- "black" # zone 4
col[p_sol < 0.5 & ICdatay$IC >= 0.5] <- "grey60" # zone 5
col[p_sol > 0.5 & ICdatay$IC > 0.5 & ICdatay$IC < 0.9] <- "grey60" # zone 5
# col[nec > 0.5 & nec < 0.8 & ICdatay$IC > 0.5] <- "black"
clabels <- logical(nrow(ICdatay))
clabels[c(8, 28, 9, 15, 30)] <- TRUE # only these labels to print

# TO ENSURE THE LABELS OF JITTERED POINTS ON TOP ARE VISIBLE
ICdatay$IC_ratification <- ifelse(ICdatay$IC > 0.8, ICdatay$IC-0.02, ICdatay$IC)

# TO ENSURE POLAND LABEL IS VISIBLE
# write similar ifelse function with multiple conditions?

## i_sol
# XYplot("~LDB*EUC + LDB*~RGOV + ~LDB*~OPPG*HRM + ~LDB*~OPPG*WPOW*WEQU +
#        ~RGOV*~HRM*WPOW*WEQU", IC_ratification, relation = "sufficiency", data = ICdatay, jitter = T, amount = 0.03, xlab = "Solution", clabels = clabels, cex = 0.8, col = "black", bg = col)

## p_sol
XYplot("WEQU + ~LDB*EUC + LDB*~RGOV + ~OPPG*HRM", IC_ratification, relation = "sufficiency", data = ICdatay, jitter = T, amount = 0.03, xlab = "Solution", clabels = clabels, cex = 0.8, col = "black", bg = col)

# COLOUR VERSION


# smmr(sol_p, outcome = "IC", match = F, cases = 6) # , term = 2)

```


```{r euler-sol-p, fig.cap="Solution (parsimonious) terms and overlaps\\label{fig:sol-euler-p}", out.width='99%'}
library(eulerr)

fit <- euler(c("role \n models"=13, "EU \n dependents"=5, "pro-EU \n governments"=4, "tame \n Catholicism"=2,
               "role \n models&tame \n Catholicism"=2, "role \n models&pro-EU \n governments&tame \n Catholicism"=1))

plot(fit, fills = "transparent", 
     labels = list(font = 2, fontsize=9), 
     quantities = list(cex = 1))

```

![Paths of Istanbul Convention ratification. The rounded rectangles name the four groupings found in our sufficiency analysis for IC ratification. The conditions, in rectangles, that comprise those groupings, are sufficient causes for IC ratification through the mechanisms, in trapezoids, that we described in our discussion of typical cases.](IC_process_graphic.png)

## Citation

<p class="buttons" style="text-align:center;">
<a class="btn btn-danger" target="_blank" href="https://www.zotero.org/save?type=doi&q=10.1177/00104140241290205">Add to Zotero <i class="bi-arrow-up-right-square"></i> </a>
</p>

```bibtex
@article{KrizsanRoggebandZeller2024,
  title={Who is Afraid of the Istanbul Convention? Explaining Opposition to and Support for Gender Equality},
  author={Krizsán, Andrea and Roggeband, Conny and Zeller, Michael C},
  journal={Comparative Political Studies},
  volume={58},
  number={10},
  pages={2161--2200},
  year={2024},
  publisher={Sage}
}
```

